Fusion Moves for Correlation Clustering

### 2014-11-11 paper/inputs/fig_fusion.tex
made fusion figure smaller

\begin{center}
\begin{figure*}[ht]
\resizebox{\linewidth}{!}{
    \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

@@

            % first segmentation as coloring
            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 1. FUSION
            \draw (2+4,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+4,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+4,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+4,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+4,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+4,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+4,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 2. FUSION
            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 3. FUSION
            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 4. FUSION
            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 5. FUSION
            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 6. FUSION
            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 7. FUSION
            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
            {
                \Large{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
            };

            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
            {
                \Large{All these node labelings encode the same partition}
            };

            \draw[black] (5,-1) -- (33,-1);

    \end{tikzpicture}
}
\caption{
todo: write me (why normal fusion does not work)
}\label{fig:fusion_abiguty}
\end{figure*}
\end{center}

>>>>

\begin{center}
\begin{figure}[ht]
\resizebox{\linewidth}{!}{
    \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

@@

            % first segmentation as coloring
            \draw (2+3.5,2+4) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+3.5,2+4) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+3.5,0+4) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+3.5,0+4) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 1. FUSION
            \draw (2+3.5,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+3.5,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+3.5,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+3.5,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+3.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+3.5,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+3.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+3.5,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 2. FUSION
            \draw (2+7,2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+7,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+7,0) node[nS,fill=red!60] (n3) {$2$}; 
            \draw (4+7,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+7,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
            \draw (4+7,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+7,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
            \draw (4+7,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 3. FUSION
            \draw (2+10.5,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+10.5,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+10.5,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+10.5,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+10.5,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+10.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+10.5,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+10.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 4. FUSION
            \draw (2+14,2) node[nS,fill=green!60] (n0) {$0$}; 
            \draw (4+14,2) node[nS,fill=blue!60] (n1) {$1$};
            \draw (2+14,0) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+14,0) node[nS,fill=blue!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+14,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+14,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+14,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+14,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 5. FUSION
            \draw (2+17.5,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+17.5,2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+17.5,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+17.5,0) node[nS,fill=red!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+17.5,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+17.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+17.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+17.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 6. FUSION
            \draw (2+21,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+21,2) node[nS,fill=green!60] (n1) {$1$};
            \draw (2+21,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+21,0) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+21,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+21,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
            \draw (2+21,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+21,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            % 7. FUSION
            \draw (2+24.5,2) node[nS,fill=blue!60] (n0) {$0$}; 
            \draw (4+24.5,2) node[nS,fill=yellow!60] (n1) {$1$};
            \draw (2+24.5,0) node[nS,fill=blue!60] (n3) {$2$}; 
            \draw (4+24.5,0) node[nS,fill=yellow!60] (n4) {$3$};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2+24.5,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
            \draw (4+24.5,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
            \draw (2+24.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
            \draw (4+24.5,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
            \path
                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
            ;

            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
            (5,-6) -- (29,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
            {
                \Large{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
            };

            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
            (5,2) -- (29,2) node [black,midway,xshift=0cm,yshift=1cm] 
            {
                \Large{All these node labelings encode the same partition}
            };

            \draw[black] (5,-1) -- (29,-1);

    \end{tikzpicture}
}
\caption{
todo: write me (why normal fusion does not work)
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}
